---
title: "RR_SVC_2019"
author: "Zhehan"
date: "October 8, 2019"
output: html_document
---
#library
```{r}
library(spectrolab)
library(readxl)
library(dplyr)
library(tidyr)
library(Hmisc)
library(corrplot)
library(ggplot2)
library(ggsci)
library(stringr)
library(hsdar)
library(rpart.plot)
library(rattle)
```

#read svc reflectance
```{r}
path_svc <- "C:/Users/zt92/Box Sync/CC_UCD_RR/SVC_disease_20190711"
sp_svc <- read_spectra(path_svc, format = "sig")
#smooth the reflectance
sp_sm <- spectrolab::smooth(sp_svc)
#get the reflectance matrix
ref_sm <- reflectance(sp_svc)
#get the wavelength vector
wavelen <- wavelengths(sp_svc)
#get the names
filename <- names(sp_sm)

#split the names
ID <- sapply(strsplit(filename, split = "_"), '[', 1)
ID <- as.numeric(ID)
Field <- sapply(strsplit(filename, split = "_"), '[', 2)
Field <- as.factor(Field)
Sample <- sapply(strsplit(filename, split = "_"), '[', 3)
Sample <- str_remove(Sample, "S")
Repeat <- sapply(strsplit(filename, split = "_"), '[', 4)
Repeat <- as.numeric(Repeat)
Class <- sapply(strsplit(filename, split = "_"), '[', 5)
Class <- str_remove(Class, ".sig")
Class <- as.factor(Class)

#create a big data frame 
df_svc <- data.frame(ref_sm)
names(df_svc) <- wavelen
df_svc$ID <- ID
df_svc$Field <- Field
df_svc$Sample <- Sample
df_svc$Repeat <- Repeat
df_svc$Class <- Class

#reorder the data frame 
df_svc <- df_svc[order(df_svc$ID),]
```

##resample to some bands that are available 
```{r}
#this just uses the subset instead of resampling 
df_svc_sb <- df_svc %>% dplyr::select(ID = ID, Field = Field, Sample = Sample, Repeat = Repeat, Class = Class, R450 = "450.3",R475 = "474.8", R480 = "480.5", R531 = "531.7", R550 = "550", R560 = "559.8", R570 = "569.6", R668 = "668.4", R670 = "669.8", R700 = "699.3", R717 = "716.7", R720 = "720.6", R740 = "740.4", R800 = "799.9", R840 = "840.1", R900 = "899.5", R970 = "970.6")
```

##functions to calculate VIs
```{r}
#ndvi.te 
ndvi.te <- function(df){
  R800 = df$R800
  R670 = df$R670
  NDVI = (R800-R670)/(R800+R670)
  return(NDVI)
}

#ndre1.te
ndre1.te <- function(df){
  R700 = df$R700
  R800 = df$R800
  NDRE1 = (R800-R700)/(R800+R700)
  return(NDRE1)
}

#ndre2.te
ndre2.te <- function(df){
  R720 = df$R720
  R800 = df$R800
  NDRE2 = (R800-R720)/(R800+R720)
  return(NDRE2)
}

#ndre3.te
ndre3.te <- function(df){
  R740 = df$R740
  R800 = df$R800
  NDRE3 = (R800-R740)/(R800+R740)
  return(NDRE3)
}

#ndre.mi
ndre.mi <- function(df){
  R717 = df$R717
  R840 = df$R840
  NDRE = (R840-R717)/(R840+R717)
  return(NDRE)
}

#ndvi.mi
ndvi.mi <- function(df){
  R840 = df$R840
  R668 = df$R668
  NDVI = (R840-R668)/(R840+R668)
  return(NDVI)
}

#tcari/osavi
tcari.osavi <- function(df){
  R700 = df$R700
  R670 = df$R670
  R550 = df$R550
  R800 = df$R800
  TCARI = 3*((R700-R670)-0.2*(R700-R550)*(R700/R670))
  OSAVI = (1+0.16)*(R800-R670)/(R800+R670+0.16)
  return(TCARI/OSAVI)
}

#mcari
mcari <- function(df){
  R700 = df$R700
  R670 = df$R670
  R550 = df$R550
  R800 = df$R800
  MCARI = ((R700-R670)-0.2*(R700-R550))*(R700/R670)
  return(MCARI)
}

#PRI
pri <- function(df){
  R531 = df$R531
  R570 = df$R570
  PRI = (R531-R570)/(R531+R570)
  return(PRI)
}

#water index 
pwi <- function(df){
  R900 = df$R900
  R970 = df$R970
  PWI = R900/R970
  return(PWI)
}


```

##function to add VIs to the dataframe 
```{r}
dfw_vis <- function(dfw){
  dfw$ndvi.te <- ndvi.te(dfw)
  dfw$ndre1.te <- ndre1.te(dfw)
  dfw$ndre2.te <- ndre2.te(dfw)
  dfw$ndre3.te <- ndre3.te(dfw)
  dfw$ndre.mi <- ndre.mi(dfw)
  dfw$ndvi.mi <- ndvi.mi(dfw)
  dfw$tcari.osavi <- tcari.osavi(dfw)
  dfw$mcari <- mcari(dfw)
  dfw$pri <- pri(dfw)
  dfw$pwi <- pwi(dfw)
  return(dfw)
}
```

##add VIs to the dataframe 
```{r}
df_svc_sb <- dfw_vis(df_svc_sb)
```

##plot all the curves together
```{r}
###change the data frame from wide to long
dfw_svc <- gather(df_svc, wavelength, reflectance, "337.5":"2515.8")
dfw_svc <- dfw_svc[order(dfw_svc$ID),]
dfw_svc$wavelength <- as.numeric(dfw_svc$wavelength)

##calculate mean and variance
a <- dfw_svc %>% group_by(Class, wavelength) %>% summarise(Mean = mean(reflectance), Vairance = var(reflectance))
str(a)
a$wavelength <- as.numeric(a$wavelength)

#plot
ggplot(a, aes(x = wavelength, y = Mean, color = Class)) + geom_line(aes(size = 2)) +ylab("Average Reflectance")+xlab("Wavelength") +
  geom_line(data = dfw_svc, aes(x = wavelength, y = reflectance, color =  Class, alpha = 0.2, size = 0.5))

ggplot(data = dfw_svc, aes(x = wavelength, y = reflectance, color = Class)) + geom_line( alpha = 0.2, size = 0.2)+ylab("Average Reflectance")+xlab("Wavelength")+ geom_line(data = a, aes(x = wavelength, y = Mean, color = Class))
```


#binary classification 
##subset to different 
```{r}
df_svc_sb$Class
df_svc_sb_h <- subset(df_svc_sb, Class == "Health")
df_svc_sb_b <- subset(df_svc_sb, Class == "Blight")
df_svc_sb_p <- subset(df_svc_sb, Class == "PWM")
```

#compare with the severity measured by photos
##visualization
```{r}
par(mfrow = c(3,3))
plot(df_svc_sb$Class, df_svc_sb$R450, main = "R450")
plot(df_svc_sb$Class, df_svc_sb$R475, main = "R475")
plot(df_svc_sb$Class, df_svc_sb$R480, main = "R480")
plot(df_svc_sb$Class, df_svc_sb$R531, main = "R531")
plot(df_svc_sb$Class, df_svc_sb$R550, main = "R550")
plot(df_svc_sb$Class, df_svc_sb$R560, main = "R560")
plot(df_svc_sb$Class, df_svc_sb$R570, main = "R570")
plot(df_svc_sb$Class, df_svc_sb$R668, main = "R668")
plot(df_svc_sb$Class, df_svc_sb$R670, main = "R670")
plot(df_svc_sb$Class, df_svc_sb$R700, main = "R700")
plot(df_svc_sb$Class, df_svc_sb$R717, main = "R717")
plot(df_svc_sb$Class, df_svc_sb$R720, main = "R720")
plot(df_svc_sb$Class, df_svc_sb$R740, main = "R740")
plot(df_svc_sb$Class, df_svc_sb$R800, main = "R800")
plot(df_svc_sb$Class, df_svc_sb$R840, main = "R840")
plot(df_svc_sb$Class, df_svc_sb$R900, main = "R900")
plot(df_svc_sb$Class, df_svc_sb$R970, main = "R970")










```
##quantification
```{r}
test_aov <- aov(ndvi.te ~ Class, data = df_svc_sb)
summary(test_aov)
TukeyHSD(test_aov)
```

#classification
##overview
```{r}
ggplot(df_svc_sb, aes(x = Class, fill = Class)) + geom_bar(stat=  "count") + ylab("Count") 
```
##preprocessing
```{r}
#correlation
cor_sb <- cor(df_svc_sb[,6:32])
par(mfrow = c(1,1))
corrplot(cor_sb, method = "color")

#set a threshold for feature selection 
highcor_sb <- findCorrelation(cor_sb, cutoff = 0.9, verbose = TRUE)
```

##split 
###training dataset and testing dataset
```{r}
set.seed(7)
Train_index <- createDataPartition(df_svc_sb$Class, p = 0.6, list=  FALSE)
#training data
train_svc_sb <- df_svc_sb[Train_index, ]
#testing data
test_svc_sb <- df_svc_sb[-Train_index, ]

```
###different columns
```{r}
train_svc_mi <- train_svc_sb[,c("ID","Field","Sample","Repeat","Class","R475", "R560", "R668", "R840", "R717", "ndvi.mi", "ndre.mi")]
test_svc_mi <- test_svc_sb[,c("ID","Field","Sample","Repeat","Class","R475", "R560", "R668", "R840", "R717", "ndvi.mi", "ndre.mi")]

train_svc_te <- train_svc_sb[,c("ID","Field","Sample","Repeat","Class","R450", "R480", "R531", "R550", "R570", "R670", "R700", "R720", "R740", "R800", "R900", "R970", "ndvi.te","ndre1.te", "ndre2.te", "ndre3.te", "tcari.osavi","mcari","pri","pwi")]
test_svc_te <- test_svc_sb[,c("ID","Field","Sample","Repeat","Class","R450", "R480", "R531", "R550", "R570", "R670", "R700", "R720", "R740", "R800", "R900", "R970", "ndvi.te","ndre1.te", "ndre2.te", "ndre3.te", "tcari.osavi","mcari","pri","pwi")]

```
##training
###random forest
```{r}
#training parameter
trainCon <- trainControl(method = "repeatedcv", number = 10, repeats = 10)

#with 5 bands and 2 VIs
RFmodel_mi <- train(Class~., data  = train_svc_mi[,5:12], method = "rf", trControl = trainCon, importance = TRUE, tunelength = 10)
print(RFmodel_mi)
varImp(RFmodel_mi)
plot(varImp(RFmodel_mi))
pred_RFmodel_mi <- predict(RFmodel_mi, test_svc_mi)
confusionMatrix(pred_RFmodel_mi, test_svc_mi$Class)

#with 5 bands only 
RFmodel_mi.2 <- train(Class~., data  = train_svc_mi[,5:10], method = "rf", trControl = trainCon, importance = TRUE, tunelength = 10)
print(RFmodel_mi.2)
varImp(RFmodel_mi.2)
pred_RFmodel_mi.2 <- predict(RFmodel_mi.2, test_svc_mi)
confusionMatrix(pred_RFmodel_mi, test_svc_mi$Class)


```
###LDA
```{r}
trainCon <- trainControl(method = "repeatedcv", number = 10, repeats = 10)
LDAmodel_mi <- train(Class~., data  = train_svc_mi[,5:12], method = "lda", trControl = trainCon, tunelength = 10)
pred_LDAmodel_mi <- predict(LDAmodel_mi, test_svc_mi)
confusionMatrix(pred_LDAmodel_mi, test_svc_mi$Class)

LDAmodel_mi.2 <- train(Class~., data  = train_svc_mi[,5:10], method = "lda", trControl = trainCon, tunelength = 10)
pred_LDAmodel_mi.2 <- predict(LDAmodel_mi.2, test_svc_mi)
confusionMatrix(pred_LDAmodel_mi.2, test_svc_mi$Class)

```
###SVM
```{r}
trainCon <- trainControl(method = "repeatedcv", number = 10, repeats = 10)

SVMLmodel_mi <- train(Class~., data  = train_svc_mi[,5:12], method = "svmLinear", trControl = trainCon, tunelength = 10)
pred_SVMLmodel_mi <- predict(SVMLmodel_mi, test_svc_mi)
confusionMatrix(pred_SVMLmodel_mi, test_svc_mi$Class)
varImp(SVMLmodel_mi)

SVMLmodel_mi.2 <- train(Class~., data  = train_svc_mi[,5:10], method = "svmLinear", trControl = trainCon, tunelength = 10)
pred_SVMLmodel_mi.2 <- predict(SVMLmodel_mi.2, test_svc_mi)
confusionMatrix(pred_SVMLmodel_mi.2, test_svc_mi$Class)

```


###Decision tree
```{r}
trainCon <- trainControl(method = "repeatedcv", number = 10, repeats = 10)

dtreemodel_mi <- train(form = Class~., data = train_svc_mi[,5:12], method = "rpart", trControl = trainCon,  parms = list(split = "information"))
rpart.plot(dtreemodel_mi$finalModel)
pred_dtreemodel_mi <- predict(dtreemodel_mi, test_svc_mi)
confusionMatrix(pred_dtreemodel_mi, test_svc_mi$Class)

dtreemodel_mi.2 <- train(form = Class~., data = train_svc_mi[,5:10], method = "rpart", trControl = trainCon,  parms = list(split = "information"))
rpart.plot(dtreemodel_mi.2$finalModel)
pred_dtreemodel_mi.2 <- predict(dtreemodel_mi.2, test_svc_mi)
confusionMatrix(pred_dtreemodel_mi.2, test_svc_mi$Class)

```


#Mapping
##read uav images
```{r}
read_uav <- function(path, stacks){
  #read raster layer, and crop with the extent
  uav_stacks <- raster::brick(file.path(path, stacks))
  #rename the bands
  names(uav_stacks) <- c("blue","green","red","rededge","nir","ndvi")
  
  return(uav_stacks)
}

path_stacks <- "Z:/CC_UCD_atRR/data2/UAV/stacks"
uav_20190718 <- read_uav(path_stacks, "RR_20190718_stacks2.tif")
```
##add ndre map
```{r}
#NDRE = (R840-R717)/(R840+R717)
uav_20190718$ndre <- (uav_20190718$nir - uav_20190718$rededge)/((uav_20190718$nir + uav_20190718$rededge))

```
##select vegetation areas
```{r}
ndvi_threshold <- 0.5
veg_20190718 <- calc(uav_20190718$ndvi, function(x){x[x<ndvi_threshold] <- NA; return(x)})

#mask 
uav_20190718_mask <- raster::mask(uav_20190718, veg_20190718)
```
##map with the trained decision tree model
```{r}
names(uav_20190718_mask) <- c("R475","R560","R668","R717","R840","ndvi.mi","ndre.mi")
uav_20190718_dis <- predict(uav_20190718_mask, dtreemodel_mi)
uav_20190718_dis_rf <- predict(uav_20190718_mask, RFmodel_mi)

#path output
#path_output <- "Z:/CC_UCD_atRR/data2/UAV/Outputs"
#writeRaster(uav_20190718_dis, file.path(path_output, "uav_20190718_disease.tif"))


#plot
##decision tree
plot(uav_20190718_dis, col = c("red","green","blue"), legend = FALSE, main = "Decision Tree Classification")
legend("topleft",legend = c("Blight","Health","PWM"), fill = c("red","green","blue"))
hist(uav_20190718_dis)
##random forest 
plot(uav_20190718_dis_rf, col = c("red","green","blue"), legend = FALSE, main = "Random Forest Classification")
legend("topleft",legend = c("Blight","Health","PWM"), fill = c("red","green","blue"))
hist(uav_20190718_dis)

```

#hsdar package
##spectral resampling
```{r}
a <- get.sensor.characteristics("RapidEye", TRUE)
plot(c(0,1)~c(330, 1200), type = "n")
```

