---
title: "Sentinel-2 time series"
author: "Zhehan"
date: "January 28, 2019"
output: html_document
---
#package
```{r}
library(raster)
library(ggplot2)
library(qdapRegex)
library(lubridate)
library(reshape2)
library(plyr)
library(corrplot)
```

#read shapefiles 
```{r}
#path_shp <- "Z:/CC_UCD_atRR/data2/BNDs"
path_shp <- "/z0/zt92/CC_UCD_RR/data2/BNDs"
#a small area that just covers RR
RR_BND_sen2 <- shapefile(file.path(path_shp, "RR_BND_sen2.shp"))
plot(RR_BND_sen2)

#The shapefile of the center of each field with a 15m buffer 
RR_center <- shapefile(file.path(path_shp, "RR_center_15mbuffer.shp"))
plot(RR_center)
```

#read historical data
```{r}
#path_his <- "Z:/CC_UCD_atRR/data2/BNDs/RR_CE_Shps_2013toPresent"
path_his <- "/z0/zt92/CC_UCD_RR/data2/BNDs/RR_CE_Shps_2013toPresent"
##2015
field_2015 <- as.data.frame(shapefile(file.path(path_his, "CE_TMW_2015.shp")))
field_2015 <- field_2015[,c("FieldID","year","block","system_cod","irrigation","cash_crop_","cash_cro_1", "cash_cro_2", "maize_mach", "maize_stov", "tomato_mac", "tomato_gre", "tomato_vin")]
##2016
field_2016 <- as.data.frame(shapefile(file.path(path_his, "CE_TMW_2016.shp")))
field_2016 <- field_2016[,c("FieldID","year","block","system_cod","irrigation","cash_crop_","cash_cro_1", "cash_cro_2", "maize_mach", "maize_stov", "tomato_mac", "tomato_gre", "tomato_vin")]
##2017
field_2017 <- as.data.frame(shapefile(file.path(path_his, "CE_TMW_2017.shp")))
field_2017 <- field_2017[,c("FieldID","year","block","system_cod","irrigation","cash_crop_","cash_cro_1", "cash_cro_2", "maize_mach", "maize_stov", "tomato_mac", "tomato_gre", "tomato_vin")]
##2018
field_2018 <- as.data.frame(shapefile(file.path(path_his, "CE_TMW_2018.shp")))
field_2018 <- field_2018[,c("FieldID","year","block","system_cod","irrigation","cash_crop_","cash_cro_1", "cash_cro_2", "maize_mach", "maize_stov", "tomato_mac", "tomato_gre", "tomato_vin")]

```


#ndvi function 
```{r}
ndvi <- function(red, nir){
  NDVI <- (nir-red)/(nir+red)
  return(NDVI)
}
```



#Read all Image files 

##(L1C 2015) read all image files from Sentinel-2 L1C
```{r}
#path_l1c <- "Z:/CC_UCD_atRR/data2/Sentinel-2/L1C"
path_l1c <- "/z0/zt92/CC_UCD_RR/data2/Sentinel-2/L1C"

#2015
sen2_l1c_ls_2015 <- as.list(list.files(file.path(path_l1c,"2015")))
sen2_l1c_ls_2015
#empty list
sen2_l1c_img_2015 <- list()
for(i in 1:length(sen2_l1c_ls_2015)){
  #get the file name
  name <- list.files(path = paste(path_l1c,"2015", sen2_l1c_ls_2015[[i]], sep = "/"), pattern = ".jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[2])
  img_3 <- raster(name_img[3])
  img_4 <- raster(name_img[4])
  img_8 <- raster(name_img[8])
  #brick them together and store in the list
  sen2_l1c_img_2015[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l1c_img_2015[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l1c_img_2015[[i]] <- raster::crop(sen2_l1c_img_2015[[i]], RR_BND_sen2)
  #names 
  names(sen2_l1c_img_2015)[i] <- qdapRegex::rm_between(sen2_l1c_ls_2015[[i]], "L1C_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l1c_img_2015)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}

```


##(L1C 2016) read all image files from Sentinel-2 L1C
```{r}
#2016
sen2_l1c_ls_2016 <- as.list(list.files(file.path(path_l1c,"2016")))
sen2_l1c_ls_2016
#empty list
sen2_l1c_img_2016 <- list()
for(i in 1:length(sen2_l1c_ls_2016)){
  #get the file name
  name <- list.files(path = paste(path_l1c,"2016", sen2_l1c_ls_2016[[i]], sep = "/"), pattern = ".jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[2])
  img_3 <- raster(name_img[3])
  img_4 <- raster(name_img[4])
  img_8 <- raster(name_img[8])
  #brick them together and store in the list
  sen2_l1c_img_2016[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l1c_img_2016[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l1c_img_2016[[i]] <- raster::crop(sen2_l1c_img_2016[[i]], RR_BND_sen2)
  #names 
  names(sen2_l1c_img_2016)[i] <- qdapRegex::rm_between(sen2_l1c_ls_2016[[i]], "L1C_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l1c_img_2016)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}

```



##(L1C 2017) read all image files from Sentinel-2 L1C
```{r}

#2017
sen2_l1c_ls_2017 <- as.list(list.files(file.path(path_l1c,"2017")))
sen2_l1c_ls_2017
#empty list
sen2_l1c_img_2017 <- list()
for(i in 1:length(sen2_l1c_ls_2017)){
  #get the file name
  name <- list.files(path = paste(path_l1c,"2017", sen2_l1c_ls_2017[[i]], sep = "/"), pattern = ".jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[2])
  img_3 <- raster(name_img[3])
  img_4 <- raster(name_img[4])
  img_8 <- raster(name_img[8])
  #brick them together and store in the list
  sen2_l1c_img_2017[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l1c_img_2017[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l1c_img_2017[[i]] <- raster::crop(sen2_l1c_img_2017[[i]], RR_BND_sen2)
  #names 
  names(sen2_l1c_img_2017)[i] <- qdapRegex::rm_between(sen2_l1c_ls_2017[[i]], "L1C_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l1c_img_2017)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}

```

##(L1C 2018) read all image files from Sentinel-2 L1C
```{r}

#2018
sen2_l1c_ls_2018 <- as.list(list.files(file.path(path_l1c,"2018")))
sen2_l1c_ls_2018
#empty list
sen2_l1c_img_2018 <- list()
for(i in 1:length(sen2_l1c_ls_2018)){
  #get the file name
  name <- list.files(path = paste(path_l1c,"2018", sen2_l1c_ls_2018[[i]], sep = "/"), pattern = ".jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[2])
  img_3 <- raster(name_img[3])
  img_4 <- raster(name_img[4])
  img_8 <- raster(name_img[8])
  #brick them together and store in the list
  sen2_l1c_img_2018[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l1c_img_2018[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l1c_img_2018[[i]] <- raster::crop(sen2_l1c_img_2018[[i]], RR_BND_sen2)
  #names 
  names(sen2_l1c_img_2018)[i] <- qdapRegex::rm_between(sen2_l1c_ls_2018[[i]], "L1C_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l1c_img_2018)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}

```

##(L2A 2015) read all image files from Sentinel-2 L2A
```{r}
#get all folder name 
#path_l2a <- "Z:/CC_UCD_atRR/data2/Sentinel-2/L2A"
path_l2a <- "/z0/zt92/CC_UCD_RR/data2/Sentinel-2/L2A"
#2015
sen2_l2a_ls_2015 <- as.list(list.files(file.path(path_l2a,"2015")))
sen2_l2a_ls_2015
#empty list
sen2_l2a_img_2015 <- list()
for(i in 1:length(sen2_l2a_ls_2015)){
  #get the file name
  name <- list.files(path = paste(path_l2a,"2015", sen2_l2a_ls_2015[[i]], sep = "/"), pattern = "_10m.jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[1])
  img_3 <- raster(name_img[2])
  img_4 <- raster(name_img[3])
  img_8 <- raster(name_img[4])
  #brick them together and store in the list
  sen2_l2a_img_2015[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l2a_img_2015[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l2a_img_2015[[i]] <- raster::crop(sen2_l2a_img_2015[[i]], RR_BND_sen2)
  #names 
  names(sen2_l2a_img_2015)[i] <- qdapRegex::rm_between(sen2_l2a_ls_2015[[i]], "L2A_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l2a_img_2015)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}
```

##(L2A 2016) read all image files from Sentinel-2 L2A
```{r}
#2016
sen2_l2a_ls_2016 <- as.list(list.files(file.path(path_l2a,"2016")))
sen2_l2a_ls_2016
#empty list
sen2_l2a_img_2016 <- list()
for(i in 1:length(sen2_l2a_ls_2016)){
  #get the file name
  name <- list.files(path = paste(path_l2a,"2016", sen2_l2a_ls_2016[[i]], sep = "/"), pattern = "_10m.jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[1])
  img_3 <- raster(name_img[2])
  img_4 <- raster(name_img[3])
  img_8 <- raster(name_img[4])
  #brick them together and store in the list
  sen2_l2a_img_2016[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l2a_img_2016[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l2a_img_2016[[i]] <- raster::crop(sen2_l2a_img_2016[[i]], RR_BND_sen2)
  #names 
  names(sen2_l2a_img_2016)[i] <- qdapRegex::rm_between(sen2_l2a_ls_2016[[i]], "L2A_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l2a_img_2016)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}
```

##(L2A 2017) read all image files from Sentinel-2 L2A
```{r}
#2017
sen2_l2a_ls_2017 <- as.list(list.files(file.path(path_l2a,"2017")))
sen2_l2a_ls_2017
#empty list
sen2_l2a_img_2017 <- list()
for(i in 1:length(sen2_l2a_ls_2017)){
  #get the file name
  name <- list.files(path = paste(path_l2a,"2017", sen2_l2a_ls_2017[[i]], sep = "/"), pattern = "_10m.jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[1])
  img_3 <- raster(name_img[2])
  img_4 <- raster(name_img[3])
  img_8 <- raster(name_img[4])
  #brick them together and store in the list
  sen2_l2a_img_2017[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l2a_img_2017[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l2a_img_2017[[i]] <- raster::crop(sen2_l2a_img_2017[[i]], RR_BND_sen2)
  #names 
  names(sen2_l2a_img_2017)[i] <- qdapRegex::rm_between(sen2_l2a_ls_2017[[i]], "L2A_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l2a_img_2017)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}
```

##(L2A 2018) read all image files from Sentinel-2 L2A
```{r}
#2018
sen2_l2a_ls_2018 <- as.list(list.files(file.path(path_l2a,"2018")))
sen2_l2a_ls_2018
#empty list
sen2_l2a_img_2018 <- list()
for(i in 1:length(sen2_l2a_ls_2018)){
  #get the file name
  name <- list.files(path = paste(path_l2a,"2018", sen2_l2a_ls_2018[[i]], sep = "/"), pattern = "_10m.jp2", recursive = TRUE, full.names = TRUE)
  #remain only the band image
  name_img <- name[grep("B0", name)]
  #4 bands 
  img_2 <- raster(name_img[1])
  img_3 <- raster(name_img[2])
  img_4 <- raster(name_img[3])
  img_8 <- raster(name_img[4])
  #brick them together and store in the list
  sen2_l2a_img_2018[[i]] <- raster::brick(img_2, img_3, img_4, img_8)
  names(sen2_l2a_img_2018[[i]]) <- c("blue", "green", "red", "nir")
  #crop with the boundary shapefile
  sen2_l2a_img_2018[[i]] <- raster::crop(sen2_l2a_img_2018[[i]], RR_BND_sen2)
  #names 
  names(sen2_l2a_img_2018)[i] <- qdapRegex::rm_between(sen2_l2a_ls_2018[[i]], "L2A_", "T1", extract = TRUE)
  #print the date
  print(names(sen2_l2a_img_2018)[i])
  #remove the intermediate products
  #rm(c(img_2,img_3, img_4, img_8))
}
```

#Calculate NDVI based on Sentinel-2 images 
##(L1C 2015) calculate ndvi and extract values for each small fields from Sentinel-2 L1C
```{r}
#2015 
##calculate ndvi
sen2_l1c_ndvi_2015 <- list()
for(i in 1:length(sen2_l1c_img_2015)){
  sen2_l1c_ndvi_2015[[i]] <- ndvi(sen2_l1c_img_2015[[i]]$red, sen2_l1c_img_2015[[i]]$nir)
}
names(sen2_l1c_ndvi_2015) <- names(sen2_l1c_img_2015)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2015_sen2_l1c <- sapply(sen2_l1c_ndvi_2015,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2015_sen2_l1c <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2015_sen2_l1c), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2015_sen2_l1c,"Product"="Sen2 L1C", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2015_sen2_l1c <- list()
for(i in 1:length(sen2_l1c_ndvi_2015)){
  NDVI_CE_mean_2015_sen2_l1c[[i]] <- data.frame("NDVI" = raster::extract(sen2_l1c_ndvi_2015[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2015_sen2_l1c) <- names(sen2_l1c_ndvi_2015)

#remove the L1C image 
rm(sen2_l1c_img_2015)
```

##(L1C 2016) calculate ndvi and extract values for each small fields from Sentinel-2 L1C
```{r}
#2016 
##calculate ndvi
sen2_l1c_ndvi_2016 <- list()
for(i in 1:length(sen2_l1c_img_2016)){
  sen2_l1c_ndvi_2016[[i]] <- ndvi(sen2_l1c_img_2016[[i]]$red, sen2_l1c_img_2016[[i]]$nir)
}
names(sen2_l1c_ndvi_2016) <- names(sen2_l1c_img_2016)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2016_sen2_l1c <- sapply(sen2_l1c_ndvi_2016,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2016_sen2_l1c <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2016_sen2_l1c), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2016_sen2_l1c,"Product"="Sen2 L1C", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2016_sen2_l1c <- list()
for(i in 1:length(sen2_l1c_ndvi_2016)){
  NDVI_CE_mean_2016_sen2_l1c[[i]] <- data.frame("NDVI" = raster::extract(sen2_l1c_ndvi_2016[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2016_sen2_l1c) <- names(sen2_l1c_ndvi_2016)

#remove the L1C image 
rm(sen2_l1c_img_2016)
```

##(L1C 2017) calculate ndvi and extract values for each small fields from Sentinel-2 L1C
```{r}
#2017 
##calculate ndvi
sen2_l1c_ndvi_2017 <- list()
for(i in 1:length(sen2_l1c_img_2017)){
  sen2_l1c_ndvi_2017[[i]] <- ndvi(sen2_l1c_img_2017[[i]]$red, sen2_l1c_img_2017[[i]]$nir)
}
names(sen2_l1c_ndvi_2017) <- names(sen2_l1c_img_2017)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2017_sen2_l1c <- sapply(sen2_l1c_ndvi_2017,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2017_sen2_l1c <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2017_sen2_l1c), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2017_sen2_l1c,"Product"="Sen2 L1C", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2017_sen2_l1c <- list()
for(i in 1:length(sen2_l1c_ndvi_2017)){
  NDVI_CE_mean_2017_sen2_l1c[[i]] <- data.frame("NDVI" = raster::extract(sen2_l1c_ndvi_2017[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2017_sen2_l1c) <- names(sen2_l1c_ndvi_2017)

#remove the L1C image 
rm(sen2_l1c_img_2017)

```

##(L1C 2018) calculate ndvi and extract values for each small fields from Sentinel-2 L1C
```{r}
#2018 
##calculate ndvi
sen2_l1c_ndvi_2018 <- list()
for(i in 1:length(sen2_l1c_img_2018)){
  sen2_l1c_ndvi_2018[[i]] <- ndvi(sen2_l1c_img_2018[[i]]$red, sen2_l1c_img_2018[[i]]$nir)
}
names(sen2_l1c_ndvi_2018) <- names(sen2_l1c_img_2018)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2018_sen2_l1c <- sapply(sen2_l1c_ndvi_2018,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2018_sen2_l1c <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2018_sen2_l1c), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2018_sen2_l1c,"Product"="Sen2 L1C", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2018_sen2_l1c <- list()
for(i in 1:length(sen2_l1c_ndvi_2018)){
  NDVI_CE_mean_2018_sen2_l1c[[i]] <- data.frame("NDVI" = raster::extract(sen2_l1c_ndvi_2018[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2018_sen2_l1c) <- names(sen2_l1c_ndvi_2018)

#remove the L1C image 
rm(sen2_l1c_img_2018)

```

##(L2A 2015) calculate ndvi and extract values for each small fields from Sentinel-2 L2A
```{r}
#ndvi <- function(red, nir){
#  NDVI <- (nir-red)/(nir+red)
#  return(NDVI)
#}

#2015 
##calculate ndvi
sen2_l2a_ndvi_2015 <- list()
for(i in 1:length(sen2_l2a_img_2015)){
  sen2_l2a_ndvi_2015[[i]] <- ndvi(sen2_l2a_img_2015[[i]]$red, sen2_l2a_img_2015[[i]]$nir)
}
names(sen2_l2a_ndvi_2015) <- names(sen2_l2a_img_2015)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2015_sen2_l2a <- sapply(sen2_l2a_ndvi_2015,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2015_sen2_l2a <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2015_sen2_l2a), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2015_sen2_l2a, "Product" = "Sen2 L2A", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2015_sen2_l2a <- list()
for(i in 1:length(sen2_l2a_ndvi_2015)){
  NDVI_CE_mean_2015_sen2_l2a[[i]] <- data.frame("NDVI" = raster::extract(sen2_l2a_ndvi_2015[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2015_sen2_l2a) <- names(sen2_l2a_ndvi_2015)


```
##(L2A 2016) calculate ndvi and extract values for each small fields from Sentinel-2 L2A
```{r}
#ndvi <- function(red, nir){
#  NDVI <- (nir-red)/(nir+red)
#  return(NDVI)
#}

#2016 
##calculate ndvi
sen2_l2a_ndvi_2016 <- list()
for(i in 1:length(sen2_l2a_img_2016)){
  sen2_l2a_ndvi_2016[[i]] <- ndvi(sen2_l2a_img_2016[[i]]$red, sen2_l2a_img_2016[[i]]$nir)
}
names(sen2_l2a_ndvi_2016) <- names(sen2_l2a_img_2016)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2016_sen2_l2a <- sapply(sen2_l2a_ndvi_2016,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2016_sen2_l2a <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2016_sen2_l2a), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2016_sen2_l2a, "Product" = "Sen2 L2A", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2016_sen2_l2a <- list()
for(i in 1:length(sen2_l2a_ndvi_2016)){
  NDVI_CE_mean_2016_sen2_l2a[[i]] <- data.frame("NDVI" = raster::extract(sen2_l2a_ndvi_2016[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2016_sen2_l2a) <- names(sen2_l2a_ndvi_2016)


```
##(L2A 2017) calculate ndvi and extract values for each small fields from Sentinel-2 L2A
```{r}
#ndvi <- function(red, nir){
#  NDVI <- (nir-red)/(nir+red)
#  return(NDVI)
#}

#2017 
##calculate ndvi
sen2_l2a_ndvi_2017 <- list()
for(i in 1:length(sen2_l2a_img_2017)){
  sen2_l2a_ndvi_2017[[i]] <- ndvi(sen2_l2a_img_2017[[i]]$red, sen2_l2a_img_2017[[i]]$nir)
}
names(sen2_l2a_ndvi_2017) <- names(sen2_l2a_img_2017)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2017_sen2_l2a <- sapply(sen2_l2a_ndvi_2017,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2017_sen2_l2a <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2017_sen2_l2a), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2017_sen2_l2a, "Product" = "Sen2 L2A", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2017_sen2_l2a <- list()
for(i in 1:length(sen2_l2a_ndvi_2017)){
  NDVI_CE_mean_2017_sen2_l2a[[i]] <- data.frame("NDVI" = raster::extract(sen2_l2a_ndvi_2017[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2017_sen2_l2a) <- names(sen2_l2a_ndvi_2017)


```

##(L2A 2018) calculate ndvi and extract values for each small fields from Sentinel-2 L2A
```{r}
#ndvi <- function(red, nir){
#  NDVI <- (nir-red)/(nir+red)
#  return(NDVI)
#}

#2018 
##calculate ndvi
sen2_l2a_ndvi_2018 <- list()
for(i in 1:length(sen2_l2a_img_2018)){
  sen2_l2a_ndvi_2018[[i]] <- ndvi(sen2_l2a_img_2018[[i]]$red, sen2_l2a_img_2018[[i]]$nir)
}
names(sen2_l2a_ndvi_2018) <- names(sen2_l2a_img_2018)
#extract data from the entire Russell Ranch 
NDVI_RR_mean_2018_sen2_l2a <- sapply(sen2_l2a_ndvi_2018,function(x) {raster::extract(x,RR_BND_sen2, mean)})

df_NDVI_RR_mean_2018_sen2_l2a <- data.frame("Date" = as.Date(names(NDVI_RR_mean_2018_sen2_l2a), "%Y%m%d"), "NDVI" = NDVI_RR_mean_2018_sen2_l2a, "Product" = "Sen2 L2A", row.names = NULL)

#extract data for each small field 
NDVI_CE_mean_2018_sen2_l2a <- list()
for(i in 1:length(sen2_l2a_ndvi_2018)){
  NDVI_CE_mean_2018_sen2_l2a[[i]] <- data.frame("NDVI" = raster::extract(sen2_l2a_ndvi_2018[[i]], RR_center, mean), "FieldID" = RR_center$FieldID)
}
names(NDVI_CE_mean_2018_sen2_l2a) <- names(sen2_l2a_ndvi_2018)


```
#Merge with historical data
##(L1C 2015) merge with historical data
```{r}
#2015
for(i in 1:length(NDVI_CE_mean_2015_sen2_l1c)){
  NDVI_CE_mean_2015_sen2_l1c[[i]] <- merge(NDVI_CE_mean_2015_sen2_l1c[[i]], field_2015, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2015_sen2_l1c <- plyr::ldply(NDVI_CE_mean_2015_sen2_l1c, data.frame)
##change to date
names(df_NDVI_CE_mean_2015_sen2_l1c)[1] <- "Date"
df_NDVI_CE_mean_2015_sen2_l1c$Date <- as.Date(df_NDVI_CE_mean_2015_sen2_l1c$Date, "%Y%m%d")

```
##(L1C 2016) merge with historical data
```{r}
#2016
for(i in 1:length(NDVI_CE_mean_2016_sen2_l1c)){
  NDVI_CE_mean_2016_sen2_l1c[[i]] <- merge(NDVI_CE_mean_2016_sen2_l1c[[i]], field_2016, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2016_sen2_l1c <- plyr::ldply(NDVI_CE_mean_2016_sen2_l1c, data.frame)
##change to date
names(df_NDVI_CE_mean_2016_sen2_l1c)[1] <- "Date"
df_NDVI_CE_mean_2016_sen2_l1c$Date <- as.Date(df_NDVI_CE_mean_2016_sen2_l1c$Date, "%Y%m%d")

```
##(L1C 2017) merge with historical data
```{r}
#2017
for(i in 1:length(NDVI_CE_mean_2017_sen2_l1c)){
  NDVI_CE_mean_2017_sen2_l1c[[i]] <- merge(NDVI_CE_mean_2017_sen2_l1c[[i]], field_2017, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2017_sen2_l1c <- plyr::ldply(NDVI_CE_mean_2017_sen2_l1c, data.frame)
##change to date
names(df_NDVI_CE_mean_2017_sen2_l1c)[1] <- "Date"
df_NDVI_CE_mean_2017_sen2_l1c$Date <- as.Date(df_NDVI_CE_mean_2017_sen2_l1c$Date, "%Y%m%d")

```

##(L1C 2018) merge with historical data
```{r}
#2018
for(i in 1:length(NDVI_CE_mean_2018_sen2_l1c)){
  NDVI_CE_mean_2018_sen2_l1c[[i]] <- merge(NDVI_CE_mean_2018_sen2_l1c[[i]], field_2018, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2018_sen2_l1c <- plyr::ldply(NDVI_CE_mean_2018_sen2_l1c, data.frame)
##change to date
names(df_NDVI_CE_mean_2018_sen2_l1c)[1] <- "Date"
df_NDVI_CE_mean_2018_sen2_l1c$Date <- as.Date(df_NDVI_CE_mean_2018_sen2_l1c$Date, "%Y%m%d")

```

##(L2A 2015) merge with historical data 
```{r}
#2015
for(i in 1:length(NDVI_CE_mean_2015_sen2_l2a)){
  NDVI_CE_mean_2015_sen2_l2a[[i]] <- merge(NDVI_CE_mean_2015_sen2_l2a[[i]], field_2015, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2015_sen2_l2a <- plyr::ldply(NDVI_CE_mean_2015_sen2_l2a, data.frame)
##change to date
names(df_NDVI_CE_mean_2015_sen2_l2a)[1] <- "Date"
df_NDVI_CE_mean_2015_sen2_l2a$Date <- as.Date(df_NDVI_CE_mean_2015_sen2_l2a$Date, "%Y%m%d")


```
##(L2A 2016) merge with historical data 
```{r}
#2016
for(i in 1:length(NDVI_CE_mean_2016_sen2_l2a)){
  NDVI_CE_mean_2016_sen2_l2a[[i]] <- merge(NDVI_CE_mean_2016_sen2_l2a[[i]], field_2016, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2016_sen2_l2a <- plyr::ldply(NDVI_CE_mean_2016_sen2_l2a, data.frame)
##change to date
names(df_NDVI_CE_mean_2016_sen2_l2a)[1] <- "Date"
df_NDVI_CE_mean_2016_sen2_l2a$Date <- as.Date(df_NDVI_CE_mean_2016_sen2_l2a$Date, "%Y%m%d")


```
##(L2A 2017) merge with historical data 
```{r}
#2017
for(i in 1:length(NDVI_CE_mean_2017_sen2_l2a)){
  NDVI_CE_mean_2017_sen2_l2a[[i]] <- merge(NDVI_CE_mean_2017_sen2_l2a[[i]], field_2017, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2017_sen2_l2a <- plyr::ldply(NDVI_CE_mean_2017_sen2_l2a, data.frame)
##change to date
names(df_NDVI_CE_mean_2017_sen2_l2a)[1] <- "Date"
df_NDVI_CE_mean_2017_sen2_l2a$Date <- as.Date(df_NDVI_CE_mean_2017_sen2_l2a$Date, "%Y%m%d")


```

##(L2A 2018) merge with historical data 
```{r}
#2018
for(i in 1:length(NDVI_CE_mean_2018_sen2_l2a)){
  NDVI_CE_mean_2018_sen2_l2a[[i]] <- merge(NDVI_CE_mean_2018_sen2_l2a[[i]], field_2018, by = "FieldID")
}
##convert it to data frame
df_NDVI_CE_mean_2018_sen2_l2a <- plyr::ldply(NDVI_CE_mean_2018_sen2_l2a, data.frame)
##change to date
names(df_NDVI_CE_mean_2018_sen2_l2a)[1] <- "Date"
df_NDVI_CE_mean_2018_sen2_l2a$Date <- as.Date(df_NDVI_CE_mean_2018_sen2_l2a$Date, "%Y%m%d")


```

#Exploratory plots 
##Entire Russell Ranch 
```{r}
#plots for the entire Russell Ranch 
##2015 
ggplot(rbind(df_NDVI_RR_mean_2015_sen2_l1c, df_NDVI_RR_mean_2015_sen2_l2a), aes(x  = Date, y = NDVI, color = Product)) + geom_point() + geom_line() +ggtitle("Russell Ranch Average NDVI from Sentinel-2 Product in 2015") + scale_x_date(date_labels = "%Y-%m", date_breaks = "1 months") + ylim(0,1)
##2016 
ggplot(rbind(df_NDVI_RR_mean_2016_sen2_l1c, df_NDVI_RR_mean_2016_sen2_l2a), aes(x  = Date, y = NDVI, color = Product)) + geom_point() + geom_line() +ggtitle("Russell Ranch Average NDVI from Sentinel-2 Product in 2016") + scale_x_date(date_labels = "%Y-%m", date_breaks = "1 months") + ylim(0,1)
##2017 
ggplot(rbind(df_NDVI_RR_mean_2017_sen2_l1c, df_NDVI_RR_mean_2017_sen2_l2a), aes(x  = Date, y = NDVI, color = Product)) + geom_point() + geom_line() +ggtitle("Russell Ranch Average NDVI from Sentinel-2 Product in 2017") + scale_x_date(date_labels = "%Y-%m", date_breaks = "1 months") + ylim(0,1)
##2018 
ggplot(rbind(df_NDVI_RR_mean_2018_sen2_l1c, df_NDVI_RR_mean_2018_sen2_l2a), aes(x  = Date, y = NDVI, color = Product)) + geom_point() + geom_line() +ggtitle("Russell Ranch Average NDVI from Sentinel-2 Product in 2018") + scale_x_date(date_labels = "%Y-%m", date_breaks = "1 months") + ylim(0,1)


```

##Individual Blocks 
###(L2A 2015) Plot for Individual Blocks 
```{r}
#2015 
##2015 tomato 
###subset with only tomato 
df_NDVI_CE_mean_2015_sen2_l2a_tomato <- subset(df_NDVI_CE_mean_2015_sen2_l2a, cash_crop_=="Tomato")
###aggregate by the system_cod
df_NDVI_CE_mean_2015_sen2_l2a_tomato <- aggregate(df_NDVI_CE_mean_2015_sen2_l2a_tomato[,c(3,13:15)], by = list(system_cod=df_NDVI_CE_mean_2015_sen2_l2a_tomato$system_cod,Date = df_NDVI_CE_mean_2015_sen2_l2a_tomato$Date ), FUN = mean)
###plot For each system_cod
ggplot(df_NDVI_CE_mean_2015_sen2_l2a_tomato, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2015") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2015-04-23"),as.Date("2015-08-12")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2015_sen2_l2a, cash_crop_=="Tomato"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2015") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2015-04-23"),as.Date("2015-08-12")))

##2015 maize
###subset with only maize 
df_NDVI_CE_mean_2015_sen2_l2a_maize <- subset(df_NDVI_CE_mean_2015_sen2_l2a, cash_crop_=="Maize")
###aggregate by the system_cod
df_NDVI_CE_mean_2015_sen2_l2a_maize <- aggregate(df_NDVI_CE_mean_2015_sen2_l2a_maize[,c(3,11,12)], by = list(system_cod=df_NDVI_CE_mean_2015_sen2_l2a_maize$system_cod,Date = df_NDVI_CE_mean_2015_sen2_l2a_maize$Date ), FUN = mean)
###plot for each system_cod
ggplot(df_NDVI_CE_mean_2015_sen2_l2a_maize, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2015") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2015-04-12"),as.Date("2015-09-24")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2015_sen2_l2a, cash_crop_=="Maize"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2015") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2015-04-12"),as.Date("2015-09-24")))
```
###(L2A 2016) Plot for Individual Blocks
```{r}
#2016 
##2016 tomato 
###subset with only tomato 
df_NDVI_CE_mean_2016_sen2_l2a_tomato <- subset(df_NDVI_CE_mean_2016_sen2_l2a, cash_crop_=="Tomato")
###aggregate by the system_cod
df_NDVI_CE_mean_2016_sen2_l2a_tomato <- aggregate(df_NDVI_CE_mean_2016_sen2_l2a_tomato[,c(3,13:15)], by = list(system_cod=df_NDVI_CE_mean_2016_sen2_l2a_tomato$system_cod,Date = df_NDVI_CE_mean_2016_sen2_l2a_tomato$Date ), FUN = mean)
###plot For each system_cod
ggplot(df_NDVI_CE_mean_2016_sen2_l2a_tomato, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2016") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2016-04-27"),as.Date("2016-08-28")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2016_sen2_l2a, cash_crop_=="Tomato"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2016") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2016-04-27"),as.Date("2016-08-28")))

##2016 maize
###subset with only maize 
df_NDVI_CE_mean_2016_sen2_l2a_maize <- subset(df_NDVI_CE_mean_2016_sen2_l2a, cash_crop_=="Maize")
###aggregate by the system_cod
df_NDVI_CE_mean_2016_sen2_l2a_maize <- aggregate(df_NDVI_CE_mean_2016_sen2_l2a_maize[,c(3,11,12)], by = list(system_cod=df_NDVI_CE_mean_2016_sen2_l2a_maize$system_cod,Date = df_NDVI_CE_mean_2016_sen2_l2a_maize$Date ), FUN = mean)
###plot for each system_cod
ggplot(df_NDVI_CE_mean_2016_sen2_l2a_maize, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2016") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2016-04-08"),as.Date("2016-09-16")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2016_sen2_l2a, cash_crop_=="Maize"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2016") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2016-04-08"),as.Date("2016-09-16")))
```
###(L2A 2017) Plot for Individual Blocks
```{r}
#2017 
##2017 tomato 
###subset with only tomato 
df_NDVI_CE_mean_2017_sen2_l2a_tomato <- subset(df_NDVI_CE_mean_2017_sen2_l2a, cash_crop_=="Tomato")
###aggregate by the system_cod
df_NDVI_CE_mean_2017_sen2_l2a_tomato <- aggregate(df_NDVI_CE_mean_2017_sen2_l2a_tomato[,c(3,13:15)], by = list(system_cod=df_NDVI_CE_mean_2017_sen2_l2a_tomato$system_cod,Date = df_NDVI_CE_mean_2017_sen2_l2a_tomato$Date ), FUN = mean)
###plot For each system_cod
ggplot(df_NDVI_CE_mean_2017_sen2_l2a_tomato, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2017") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2017-05-01"),as.Date("2017-08-24")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2017_sen2_l2a, cash_crop_=="Tomato"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2017") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2017-05-01"),as.Date("2017-08-24")))

##2017 maize
###subset with only maize 
df_NDVI_CE_mean_2017_sen2_l2a_maize <- subset(df_NDVI_CE_mean_2017_sen2_l2a, cash_crop_=="Maize")
###aggregate by the system_cod
df_NDVI_CE_mean_2017_sen2_l2a_maize <- aggregate(df_NDVI_CE_mean_2017_sen2_l2a_maize[,c(3,11,12)], by = list(system_cod=df_NDVI_CE_mean_2017_sen2_l2a_maize$system_cod,Date = df_NDVI_CE_mean_2017_sen2_l2a_maize$Date ), FUN = mean)
###plot for each system_cod
ggplot(df_NDVI_CE_mean_2017_sen2_l2a_maize, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2017") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2017-04-24"),as.Date("2017-09-19")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2017_sen2_l2a, cash_crop_=="Maize"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2017") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2017-04-24"),as.Date("2017-09-19")))
```
###(L2A 2018) Plot for Individual Blocks
```{r}
#2018 
##2018 tomato 
###subset with only tomato 
df_NDVI_CE_mean_2018_sen2_l2a_tomato <- subset(df_NDVI_CE_mean_2018_sen2_l2a, cash_crop_=="Tomato")
###aggregate by the system_cod
df_NDVI_CE_mean_2018_sen2_l2a_tomato <- aggregate(df_NDVI_CE_mean_2018_sen2_l2a_tomato[,c(3,13:15)], by = list(system_cod=df_NDVI_CE_mean_2018_sen2_l2a_tomato$system_cod,Date = df_NDVI_CE_mean_2018_sen2_l2a_tomato$Date ), FUN = mean)
###plot For each system_cod
ggplot(df_NDVI_CE_mean_2018_sen2_l2a_tomato, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2018") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2018-05-01"),as.Date("2018-08-24")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2018_sen2_l2a, cash_crop_=="Tomato"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Tomato Field NDVI from L2A Sentinel-2 Products in 2018") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2018-05-01"),as.Date("2018-08-24")))

##2018 maize
###subset with only maize 
df_NDVI_CE_mean_2018_sen2_l2a_maize <- subset(df_NDVI_CE_mean_2018_sen2_l2a, cash_crop_=="Maize")
###aggregate by the system_cod
df_NDVI_CE_mean_2018_sen2_l2a_maize <- aggregate(df_NDVI_CE_mean_2018_sen2_l2a_maize[,c(3,11,12)], by = list(system_cod=df_NDVI_CE_mean_2018_sen2_l2a_maize$system_cod,Date = df_NDVI_CE_mean_2018_sen2_l2a_maize$Date ), FUN = mean)
###plot for each system_cod
ggplot(df_NDVI_CE_mean_2018_sen2_l2a_maize, aes(y=NDVI,x=Date, color = system_cod)) + geom_point()+geom_line() + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2018") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2018-04-24"),as.Date("2018-09-19")))
###plot for each field 
ggplot(subset(df_NDVI_CE_mean_2018_sen2_l2a, cash_crop_=="Maize"), aes(y=NDVI, x=Date, group=FieldID)) + geom_point(aes(color = system_cod)) + geom_line(aes(color = system_cod)) + scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 months") + ggtitle("Maize Field NDVI from L2A Sentinel-2 Products in 2018") + ylim(0,1) + geom_vline(xintercept = c(as.Date("2018-04-24"),as.Date("2018-09-19")))
```

#Compare with historical yield data
```{r}

```


